---
title: "p8105_HW5"
author: "Yongzi Yu yy3103"
output: github_document
---

I'm an R Markdown document! 

```{r}
library(tidyverse)
library(broom)
library(purrr)
```
# Problem1


#load data
homicide= 
  read_csv("./homicide-data.csv")%>%
  janitor::clean_names() %>%
  mutate(
    city_state = paste(city,",",state)
  ) #create a variable



#describe the raw data set



#obtain total number of homicides and unsolved
summary_total=
  homicide %>%
  group_by(city) %>%
  summarise(total=n())

summary_unsolved=
  homicide %>%
  filter(disposition =="Closed without arrest" |disposition == "Open/No arrest") %>%
  group_by(city) %>%
  summarise(total=n())

#prop test for Baltimore
bal_total=
  summary_total %>%
  filter(city == "Baltimore")
bal_unsolved=
  summary_unsolved %>%
  filter(city == "Baltimore")

res=
  prop.test(x=bal_unsolved$total,n=bal_total$total)
res
res %>%
  broom::tidy()
res 


  


# Problem2
```{r}
files=
  list.files (path = "./data")
files

file_data=
  list.files (path = "./data") %>%
  map_df(read_csv)
file_data

combine=cbind(files,file_data)
combine

tidy=
  combine%>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value"
  )
tidy

```

# Problem 3
```{r}
library(tidyverse)
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
iris_with_missing

missing = function(x) {
  if (is.character(x$Species)) {
    x$Species %>% replace_na('abc')
  }
  else {for (i in 1:4){
    x[,i][is.na(x[,i])]=mean(x[,i],na.rm=TRUE)
  }
  }
}

a=missing(iris_with_missing)
a
```